Kids PM Summary

### 2019-12-20 home_child_data_cleaning.Rmd
PM cleaning
Cleaning updates

#write_rds(kids_ids, "Output/kids_linked_ids.rds")
```

@@

#write_rds(kids_demographics, "Output/kids_combined_demographics.rds")
```

>>>>

#write_rds(kids_ids, "Output/kids_linked_ids.rds")

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
```

@@

#write_rds(kids_demographics, "Output/kids_combined_demographics.rds")

kids_demographics <- read_rds("Output/kids_combined_demographics.rds")
```

### 2019-12-20 pm_summary.Rmd
Cleaning updates

# Summary stats
```{r}
pm_summary <- kids_pm %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(sampling_day) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```

>>>>

# Summary stats
```{r}
pm_summary <- kids_pm %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```
